%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience }


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {\href{https://atlas.cern/}{\textit{https://atlas.cern/}}} % Job title
    {CERN - European Organization for Nuclear Research} % Organization
    {Infrastructure Architect - Internship} % Location
    {Feb.2021 - Aug. 2021 | Geneva,  Switzerland} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Trigger and Data Acquisition team at ATLAS experiment}
        \item {Migrating current data flow services to a microservices architecture using technologies as Docker and Kubernetes}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {\href{https://hyperloopupv.com/}{\textit{https://hyperloopupv.com/}}} % Job title
    {Hyperloop UPV} % Organization
    {Lead Software Engineer} % Location
    {Sep. 2018 - Feb. 2020 | Valencia, Spain} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Innovation award at the IV Hyperloop Pod Competition organized by SpaceX, which is one of the most \\demanding engineering competitions.}
        \item {I led the development of the telemetry system, graphical user interface, middleware and DevOps.}
        \item {This work successfully passed all SpaceX tests and was the best among all the teams.}
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
    {\href{https://www.linkedin.com/company/acmupv/}{\textit{https://www.linkedin.com/company/acmupv/}}} % Job title
    {ACM UPV - Association for Computing Machinery} % Organization
    {Organizing Member} % Location
    {Sep. 2018 - Jan. 2021 | Valencia, Spain} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {I organized events, conferences and competitions in the field of computer science at my university}
        \item {I gave some workshops about Git and chatbots}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
