\cvsection{Honors \& Awards }
\vspace{5mm} 
\newline
INTERNATIONAL
\begin{cventries}
    \cventry
        {\href{http://bit.ly/hateful-memes-lb}{\textit{http://bit.ly/hateful-memes-lb}}} % Job title
        {7th Position at Facebook Hateful Memes} % Organization
        {Facebook AI, NeurIPS Competition} % Location
        {May. 2020 - Oct. 2020} % Date(s)
        {\begin{cvitems} % Description(s) bullet points
        \item {Competition overview:  \href{https://ai.facebook.com/blog/hateful-memes-challenge-and-data-set/}{\textit{https://ai.facebook.com/blog/hateful-memes-challenge-and-data-set/}} }
        \item {Our solution had the 7th highest AUC and the 2nd highest ACC score among 3,173 participants}
        \item {My team solution: \href{https://github.com/VictorCallejas/FB_MMHM}{\textit{GitHub}}}
        \end{cvitems}}
    \cventry
        {\href{https://bit.ly/junction-varian}{\textit{https://bit.ly/junction-varian}}} % Job title
        {Challenge Winner at Europe Junction Hackathon} % Organization
        {Junction - Helsinki, Finland} % Location
        {2019} % Date(s)
        {\begin{cvitems} % Description(s) bullet points
        \item {My team and I won the healthcare challenge proposed by Varian Medical Systems, developing a graphical user interface during the course of the hackathon to coordinate the job of the medic and physician.}
    \end{cvitems} }
     \cventry
        {\href{https://bit.ly/noticia-upv-spaceapps}{\textit{https://bit.ly/noticia-upv-spaceapps}}} % Job title
        {Local Winner at Space Apps Hackathon} % Organization
        {NASA} % Location
        {2018} % Date(s)
        {\begin{cvitems}
        \item Local Second prize and Best Concept Mission.	
    	\item I developed a space assistant chatbot that answers questions related to space and informs about new space rocket launches. This bot also implemented a deepart feature to fusion a picture of your own with one of NASA Space Gallery.
    	\end{cvitems}}

\end{cventries}

\vspace{3mm}

UNIVERSITY

\begin{cventries}

  \cventry
    {} % Job title
    {1st Prize at UPV Advent Of Code} % Organization
    {Universidad Politécnica de Valencia - ACM UPV} % Location
    {2019} % Date(s)
    {\begin{cvitems}
    \item Code competition at my university for second year students.
    \end{cvitems}}

  \cventry
    {\href{http://bit.ly/ideasV-ep}{\textit{http://bit.ly/ideasV-ep}}} % Job title
    {Ideas UPV Challenge} % Organization
    {Universidad Politécnica de Valencia - IDEAS UPV} % Location
    {2017, 2018, 2019} % Date(s)
    {\begin{cvitems}
    \item This is a university entrepreneurship contest where companies come and propose a challenge to be solve by student teams
    \item I won three editions of this competition. 
    \item III edition (2017): I proposed a real time and dynamic system to control the semaphores, mainly by using computer vision to obtain the volume of cars in the roads thanks to cameras at the top of the semaphores.
    \item V edition (2018): My team and I proposed and make a demo about a non-instrusive way of measuring biomedical parameters in e-sports players through computer vision by using the webcam. With the colaboration of MAD LIONS E.C.
    \item VIII edition (2019): I developed a telephonic bot to automate real state visits for agents. I used IBM Watson and Twilio services.
    \end{cvitems}}
    
  \cventry
    {} % Job title
    {1st Prize at the III UPV Datathon} % Organization
    {Universidad Politécnica de Valencia - DATA UPV} % Location
    {2018} % Date(s)
    {\begin{cvitems}
    \item  I developed a machine learning model to predict pollution and pollen in the city of Valencia.
    \end{cvitems}}

\end{cventries}